\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{hyperref}

\title{UnBox3D TestRail Report -- Snapshot 2}
\author{Alexander Ramirez \\ Vivian Casas \\ Jacky Lim \\ Nicholas Sisneros \\ Vince Wang}
\date{}

\begin{document}
\maketitle

\section{Overview}

This Snapshot 2 TestRail report documents the early testing of UnBox3D.  
At this stage, implemented features include:

\begin{itemize}
  \item Splash screen and placeholder UI with an Import button and viewport.
  \item Basic model import using Assimp for .obj files.
  \item Initial OpenGL rendering using OpenTK.
\end{itemize}

The objective of this testing cycle was to verify that the application launches successfully, imports simple .obj files, and renders them without crashing.

\section{Test Environment}

\begin{itemize}
  \item OS: Windows 10 / 11 (64-bit)
  \item Framework: .NET
  \item Graphics: OpenGL via OpenTK
  \item Build: Snapshot 2 tagged build
  \item Test Models: cube.obj, low-poly.obj, invalid.txt
\end{itemize}

\section{Test Cases}

\setlength{\extrarowheight}{2pt}

\begin{longtable}{p{1.7cm} p{3.0cm} p{3.0cm} p{6.0cm} p{3.0cm} p{0.9cm}}
\toprule
\textbf{ID} & \textbf{Title} & \textbf{Preconditions} & \textbf{Steps} & \textbf{Expected Result} & \textbf{Pr.} \\
\midrule
\endfirsthead
\toprule
\textbf{ID} & \textbf{Title} & \textbf{Preconditions} & \textbf{Steps} & \textbf{Expected Result} & \textbf{Pr.} \\
\midrule
\endhead

TC-2-01 & Application Launch & Build installed & 
1. Open executable. &
Application launches to splash screen then main UI. & H \\ 
\midrule

TC-2-02 & UI Layout Loads & App launched & 
Observe main window. &
UI displays Import button + viewport. & H \\ 
\midrule

TC-2-03 & Import Button Enabled & App launched & 
Check Import button state. &
Button is active and clickable. & H \\ 
\midrule

TC-2-04 & Valid .obj Import & Valid .obj available & 
1. Click Import  
2. Select .obj file &
Model loads without error. & H \\
\midrule

TC-2-05 & Model Visible in Viewport & Model imported & 
Observe viewport. &
Model renders centered and visible. & H \\
\midrule

TC-2-06 & Invalid File Handling & Invalid file available & 
1. Import invalid file &
App shows clear error; no crash. & M \\
\midrule

TC-2-07 & Large Model Stability & Large .obj available &
1. Import large model &
App remains responsive and does not crash. & M \\
\midrule

TC-2-08 & Basic Camera Interaction & Model loaded &
Attempt rotate/zoom (if implemented). &
If implemented: interacts smoothly.  
If not: app safely ignores. & L \\
\bottomrule
\end{longtable}

\section{Test Run Results}

\begin{tabularx}{\textwidth}{p{1.7cm} p{2.5cm} p{3cm} X}
\toprule
\textbf{ID} & \textbf{Result} & \textbf{Tester} & \textbf{Notes} \\
\midrule
TC-2-01 & Passed & Alexander Ramirez & Launches in ~2 seconds. \\
TC-2-02 & Passed & Vivian Casas & UI elements load correctly. \\
TC-2-03 & Passed & Jacky Lim & Import button active by default. \\
TC-2-04 & Passed & Nicholas Sisneros & cube.obj imports successfully. \\
TC-2-05 & Passed & Nicholas Sisneros & Viewport displays model correctly. \\
TC-2-06 & Failed & Alexander Ramirez & Error message unclear; behavior correct. \\
TC-2-07 & Passed & Vivian Casas & Large model import slow but stable. \\
TC-2-08 & Blocked & Jacky Lim & Camera not yet implemented. \\
\bottomrule
\end{tabularx}

\section{Metrics}

\begin{itemize}
    \item Total Tests: 8
    \item Passed: 6
    \item Failed: 1
    \item Blocked: 1
    \item Pass Rate: 75\%
\end{itemize}

\section{Conclusion}

Snapshot 2 confirms that import + rendering works correctly and the base UI behaves as expected. Camera features will be added next snapshot.

\end{document}
