\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{longtable}

\title{UnBox3D TestRail Report -- Snapshot 3}
\author{Alexander Ramirez \\ Vivian Casas \\ Jacky Lim \\ Nicholas Sisneros \\ Vince Wang}
\date{}

\begin{document}
\maketitle

\section{Overview}

Snapshot 3 adds:

\begin{itemize}
  \item Bounding-box filtering to remove small mesh parts.
  \item Mesh simplification using Blender’s decimation modifier.
  \item Retesting of all Snapshot 2 functionality.
\end{itemize}

This test cycle validates model processing and ensures rendering remains stable following geometry modifications.

\section{Test Environment}
\begin{itemize}
  \item OS: Windows 10/11
  \item Blender installed
  \item OpenTK/OpenGL rendering
  \item Snapshot 3 build
\end{itemize}

\section{Test Cases}
\setlength{\extrarowheight}{2pt}

\begin{longtable}{p{1.7cm} p{3.2cm} p{3.0cm} p{6.0cm} p{3.0cm} p{0.9cm}}
\toprule
\textbf{ID} & \textbf{Title} & \textbf{Preconditions} & \textbf{Steps} & \textbf{Expected Result} & \textbf{Pr.} \\
\midrule
\endfirsthead
\toprule
\textbf{ID} & \textbf{Title} & \textbf{Preconditions} & \textbf{Steps} & \textbf{Expected Result} & \textbf{Pr.} \\
\midrule
\endhead

TC-3-01 & Regression: Launch + UI & Build installed &
Launch app. &
UI loads successfully. & H \\
\midrule

TC-3-02 & Regression: Import & Valid .obj &
Import file. &
Imports and renders normally. & H \\
\midrule

TC-3-03 & Small Parts Removed & Multi-object scene &
1. Import scene  
2. Apply filter &
Small objects removed based on threshold. & H \\
\midrule

TC-3-04 & Filter Threshold & Filter adjustable &
1. Import  
2. Raise threshold  
3. Lower threshold &
Higher threshold removes more, lower removes fewer. & M \\
\midrule

TC-3-05 & Filter Disabled & Filter off &
Import scene &
No filtering occurs. & M \\
\midrule

TC-3-06 & Mesh Decimation & Blender installed &
1. Import mesh  
2. Apply decimation &
Polygon count reduced. & H \\
\midrule

TC-3-07 & Blender Missing & Blender missing &
Trigger decimation &
Clear error; app does not crash. & M \\
\midrule

TC-3-08 & Combined Performance & Scene loaded &
Filter → Decimate &
App stays responsive. & M \\
\midrule

TC-3-09 & Camera Interaction & Processed mesh loaded &
Move camera &
Camera interacts properly. & M \\
\bottomrule
\end{longtable}

\section{Test Run Results}

\begin{tabularx}{\textwidth}{p{1.7cm} p{2.5cm} p{3.0cm} X}
\toprule
ID & Result & Tester & Notes \\
\midrule
TC-3-01 & Passed & Vivian Casas & UI stable. \\
TC-3-02 & Passed & Nicholas Sisneros & Rendering unchanged. \\
TC-3-03 & Passed & Alexander Ramirez & Small parts removed correctly. \\
TC-3-04 & Failed & Jacky Lim & Slider lacks visible numeric value. \\
TC-3-05 & Passed & Vince Wang & Correct behavior. \\
TC-3-06 & Passed & Vivian Casas & Polygon count reduced ~50\%. \\
TC-3-07 & Passed & Jacky Lim & Error message readable. \\
TC-3-08 & Passed & Nicholas Sisneros & Slight CPU spike but stable. \\
TC-3-09 & Passed & Vince Wang & Camera works smoothly. \\
\bottomrule
\end{tabularx}

\section{Metrics}

\begin{itemize}
    \item Total Tests: 9
    \item Passed: 8
    \item Failed: 1
    \item Pass Rate: 88.9\%
\end{itemize}

\section{Conclusion}

Snapshot 3 confirms stable model manipulation via filtering and decimation, with only minor UI improvements needed.

\end{document}
