\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{longtable}

\title{UnBox3D TestRail Report -- Snapshot 4 (Final)}
\author{Alexander Ramirez \\ Vivian Casas \\ Jacky Lim \\ Nicholas Sisneros \\ Vince Wang}
\date{}

\begin{document}
\maketitle

\section{Overview}

Snapshot 4 adds:

\begin{itemize}
  \item 2D layout export via Blender paper model exporter (.svg)
  \item Final UI polish
  \item Full end-to-end workflow testing
\end{itemize}

This snapshot validates final deliverable readiness.

\section{Test Environment}
\begin{itemize}
  \item Windows 10/11
  \item Blender with paper model exporter add-on
  \item OpenTK/OpenGL rendering
  \item Snapshot 4 final build
\end{itemize}

\section{Test Cases}

\begin{longtable}{p{1.8cm} p{3.2cm} p{3.0cm} p{6.0cm} p{3cm} p{0.9cm}}
\toprule
ID & Title & Preconditions & Steps & Expected Result & Pr. \\
\midrule
\endfirsthead
\toprule
ID & Title & Preconditions & Steps & Expected Result & Pr. \\
\midrule
\endhead

TC-4-01 & Regression: Import & Final build installed &
Import cube.obj &
Model loads + renders. & H \\
\midrule

TC-4-02 & Pipeline Regression & Scene exists &
Filter → Decimate &
Pipeline produces stable output. & H \\
\midrule

TC-4-03 & SVG Export (Simple) & Blender configured &
1. Import cube  
2. Export 2D layout &
.svg generated without error. & H \\
\midrule

TC-4-04 & SVG Opens Correctly & .svg exists &
Open in browser &
Renders flattened layout properly. & H \\
\midrule

TC-4-05 & Export Medium Model & Medium model exists &
Import → Filter → Decimate → Export &
.svg generated; completes reasonably fast. & H \\
\midrule

TC-4-06 & Invalid Export Path & User selects invalid directory &
Trigger export &
Clear error, no crash. & M \\
\midrule

TC-4-07 & UI Polish & Final UI loaded &
Inspect UI &
No placeholder text, consistent layout. & M \\
\midrule

TC-4-08 & Many Small Parts & Complex scene &
Import → Filter → Export &
Stable behavior; output created. & M \\
\midrule

TC-4-09 & Full E2E Workflow & Final build &
Import → Filter → Decimate → Export → View &
Successful full pipeline. & H \\
\midrule

TC-4-10 & Exporter Failure Handling & Break exporter intentionally &
Attempt export &
Graceful error message. & M \\
\bottomrule
\end{longtable}

\section{Test Run Results}

\begin{tabularx}{\textwidth}{p{1.8cm} p{2.5cm} p{3cm} X}
\toprule
ID & Result & Tester & Notes \\
\midrule
TC-4-01 & Passed & Alexander Ramirez & No regressions. \\
TC-4-02 & Passed & Vivian Casas & Output stable. \\
TC-4-03 & Passed & Jacky Lim & SVG looks clean. \\
TC-4-04 & Passed & Nicholas Sisneros & Opens in Chrome + Inkscape. \\
TC-4-05 & Passed & Vince Wang & Export ~12 seconds. \\
TC-4-06 & Passed & Vivian Casas & Error dialog correct. \\
TC-4-07 & Passed & Nicholas Sisneros & UI polished and consistent. \\
TC-4-08 & Passed & Alexander Ramirez & Heavy model handled. \\
TC-4-09 & Passed & Jacky Lim & Pipeline complete. \\
TC-4-10 & Passed & Vince Wang & Error handled safely. \\
\bottomrule
\end{tabularx}

\section{Metrics}
\begin{itemize}
    \item Total Tests: 10
    \item Passed: 10
    \item Failed: 0
    \item Pass Rate: 100\%
\end{itemize}

\section{Conclusion}

All final pipeline features function correctly, including 2D export. UnBox3D meets the expected deliverables for the CS3338 final project.

\end{document}
